A Comparative Quality Metric for Untargeted Fuzzing with Logic State Coverage

### 2024-06-06 paper/main.tex
checkpt

\pp{Interestingness in practice}
%
As the interestingness $\Pr(\mathrm{UA} \mid \mathrm{N})$ is the expectation of
an \emph{unobserved} behavior, there is no direct way to measure
interestingness. 
%
However, the common usage of corpus minimization \cite{todo} and branch hit
count buckets \cite{todo} in untargeted fuzzing suggests that a program behavior
is less likely to be \emph{unknown abnormal} (i.e., less interesting) if its
mutation base input is highly repetitive.
%in modern untargeted fuzzing.
%
The rationales are: (i) if a fewer repetition was normal,
more repetition is also likely normal and (ii) even if it was abnormal, it is 
not unknown if it corresponds to pre-observed less-repetition counterparts.

@@

Logic states coalesce the program behaviors in a fewer logic states as the
behaviors contain more branch repetitions, resulting in smaller (larger)
logic state coverage as it observes more uninteresting (interesting) program
behaviors.

@@

The colored boxes in \autoref{f:repr} suggest the increasing size of logic
states as their constituent program behaviors involve more repetitive branches.
To be specific, a logic state covers a progressively larger volume in the logic
space (i.e., \cbox{black} $\rightarrow$ \cbox{red}/\cbox{green}/\cbox{blue}
$\rightarrow$ \cbox{yellow}/\cbox{cyan}/\cbox{magenta} $\rightarrow$
\cbox{gray}) as it contains more repetitive branches (i.e., 0 $\rightarrow$ 1
$\rightarrow$ 2 $\rightarrow$ 3 repetitive branches). 
%
This results in repetitive (i.e., uninteresting) program states packed
to fewer logic states, suppressing (boosting) logic state coverage as it observes more
uninteresting (interesting) behaviors.
%\footnote{It is worth noting that a coordinate in the grid does
%\emph{not} represent one program behavior. For example, a coordinate (1, 1, 0)
%represents two program behaviors, $b_1$ before $b_2$ and $b_2$ before $b_1$.
%However, it does not affect the relative size of visualized logic states because
%a coordinate only has more program behaviors as it gets further from the
%origin.}

>>>>

\pp{Interestingness in practice}
%
As the interestingness $\Pr(\mathrm{UA} \mid \mathrm{N})$ is the expectation of
an \emph{unobserved} behavior, there is no direct way to measure
interestingness. 
%
However, the common usage of corpus minimization
\cite{libfuzzer,efffuzz,herrera2021seedsel,herrera2021seedsel} and branch hit
count buckets \cite{afl,libfuzzer} in untargeted fuzzing suggests that a program behavior
is less likely to be \emph{unknown abnormal} (i.e., less interesting) if its
mutation base input is highly repetitive.
%in modern untargeted fuzzing.
%
The rationales are: (i) if a fewer repetition was normal,
more repetition is also likely normal and (ii) even if it was abnormal, it is 
not unknown if it corresponds to pre-observed less-repetition counterparts.

@@

Logic states coalesce less interesting program behaviors that exhibit more
branch repetitions in a fewer logic states, resulting in smaller (larger) logic
state coverage as it observes more uninteresting (interesting) program
behaviors.

@@

The colored boxes in \autoref{f:repr} suggest the increasing size of logic
states as their constituent program behaviors involve more repetitive branches.
To be specific, a logic state covers a progressively larger volume 
%in the logic space 
(i.e., \cbox{black} $\rightarrow$ \cbox{red}/\cbox{green}/\cbox{blue}
$\rightarrow$ \cbox{yellow}/\cbox{cyan}/\cbox{magenta} $\rightarrow$
\cbox{gray}) as it contains more repetitive branches (i.e., 0 $\rightarrow$ 1
$\rightarrow$ 2 $\rightarrow$ 3 repetitive branches). 
%
This results in repetitive (i.e., uninteresting) program states packed
to fewer logic states, suppressing (boosting) logic state coverage as it observes more
uninteresting (interesting) behaviors.
%\footnote{It is worth noting that a coordinate in the grid does
%\emph{not} represent one program behavior. For example, a coordinate (1, 1, 0)
%represents two program behaviors, $b_1$ before $b_2$ and $b_2$ before $b_1$.
%However, it does not affect the relative size of visualized logic states because
%a coordinate only has more program behaviors as it gets further from the
%origin.}
